On The Benefits of Magnitude Estimation Relevance Assessments for Information Retrieval Evaluation

### 2016-09-16 response.tex

We thank the reviewers for their constructive feedback and suggestions
for improvements.
Our responses to particular comments are outlined below.
Changes in the manuscript have been highlighted in red font to make
them easy to spot.

\section{Reviewer 1}

In the footer on the first page, please add a concise statement of
the paper's addition after ``This paper is a revised and extended
version of [Turpin et al. 2015]; it adds XXX." By the way, you
should use [Author year] when you refer to a publication and Author
[year] when you refer to the author (citep{xxx} and citet{xxx},
respectively).

\comment{The citation style has been fixed, thank you. A detailed list of changes has
been added at the end of  Section 2.2, in line with the next
item.}

@@

In the related work section, please make precise how the TOIS
submission differs from the earlier SIGIR 2015 paper.

\comment{A paragraph has been added at the end of Section 2.2 to do this.}

### 2016-09-16 0_abstract.tex
Abstract + minor

Magnitude estimation is a psychophysical scaling technique for the
measurement of sensation, where observers assign numbers to stimuli in
response to their perceived intensity.
We investigate the use of magnitude estimation for judging the
relevance of documents for information retrieval
evaluation, carrying out a large-scale user study across 18 TREC topics
and collecting
over 50,000 magnitude estimation judgments using crowdsourcing.
Our analysis shows that, on average, magnitude estimation judgments are
rank-aligned with ordinal judgments made by expert relevance assessors.
%An advantage of magnitude estimation is that users can chose their own
%scale for judgments, allowing deeper investigations of user perceptions
%than when categorical scales are used.

>>>>

Magnitude estimation is a psychophysical scaling technique for the
measurement of sensation, where observers assign numbers to stimuli in
response to their perceived intensity.
We investigate the use of magnitude estimation for judging the
relevance of documents for information retrieval
evaluation, carrying out a large-scale user study across 18 TREC topics
and collecting
over 50,000 magnitude estimation judgments using crowdsourcing.
%
Our analysis shows that magnitude estimation judgments 
\textcolor{red}{ can be
reliably collected using crowdsourcing,  are competitive in terms of
assessor cost, and 
}, on average, they are
rank-aligned with ordinal judgments made by expert relevance assessors.

%An advantage of magnitude estimation is that users can chose their own
%scale for judgments, allowing deeper investigations of user perceptions
%than when categorical scales are used.
